Physcraper: A Python package for continually updated phylogenetic trees using the Open Tree of Life

### 2021-04-22 sources/bmc_template_submission/bmc_article.tex
MK edits page 8 and 9

\address[id=aff1]{%                           % unique id
  \orgdiv{School of Natural Sciences},             % department, if any
  \orgname{University of California},          % university, etc
  \city{Merced},                              % city
  \cny{USA}                                    % country
}
\address[id=aff2]{%
  \orgdiv{Department of Botany, Faculty of Science},
  \orgname{Charles University},
  %\street{},
  %\postcode{}
  \city{Prague },
  \cny{Czech Republic}
}

@@

@@

%% Biological plausibility of example??
The updated holly tree is based on a single marker, so we expect for it to be
not as well resolved as trees from studies using multiple markers. Although not perfect,
we think the tree seems biologically reasonable in different ways. All samples
corresponding to the ingroup cluster together forming a monophyletic group. We also
note that samples belonging to the same \textit{Ilex} species also cluster together forming
monophyletic groups. A notable exception is \textit{Ilex theeizans}, which appears as
non-monophyletic in the updated tree and the original Gottlieb et al. 2005 tree.
%This suggests that the samples might represent two ifferent species, but further
analyses should be conducted
A visual comparison of the Yao et al. 2020 tree and the original Gottlieb et al. 2005 tree suggests
that the relationships within the genus \textit{Ilex} are still being determined, and that
increased taxon sampling is helping with it.

@@

\section*{Conclusions}
Data repositories hold more information than meets the eye.
Beyond the main data, they are rich sources of metadata that can be leveraged
for the advantage of all areas of biology as well as the advancement of scientific
policy and applications.
Initial ideas about the data are constantly changed by results from new analyses.
Physcraper provides a framework for reproducible phylogenetics that has the
potential to consistently provide context for these ideas, highlighting the
importance of data sharing and open science in the field, biology and science.

@@

\textbf{Project name:} Physcraper

@@

\textbf{OpenTree:} The Open Tree of Life project

@@

The datasets generated and analysed during the current study are available in
the repositories "physcraper" containing the source code,
\href{https://github.com/McTavishLab/physcraper}{https://github.com/McTavishLab/physcraper};
"physcraperex" containing the examples,
\href{https://github.com/McTavishLab/physcraperex}{https://github.com/McTavishLab/physcraperex};
and, "physcraper\_ms" containing this reproducible manuscript,
\href{https://github.com/McTavishLab/physcraper\_ms}{https://github.com/McTavishLab/physcraper\_ms}.

@@

\section*{Acknowledgements}
We thank the members of the OpenTree development team and the "short bar" Science
and Engineering Building 1, UCM, joint lab paper discussion group for valuable
comments on this manuscript. We thank the valuable comments of David Posada, Rutger Vos,
and an anonymous reviewer that greatly improved earlier versions of this manuscript.

>>>>

\address[id=aff1]{%                           % unique id
  \orgdiv{School of Natural Sciences},             % department, if any
  \orgname{University of California},          % university, etc
  \city{Merced},                              % city
  \cny{USA}                                    % country
}
\address[id=aff2]{%
  \orgdiv{Department of Botany, Faculty of Science},
  \orgname{Charles University},
  %\street{},
  %\postcode{}
  \city{Prague},
  \cny{Czech Republic}
}

@@

%% Biological plausibility of example??
Our example application of Physcraper to update a holly phylogeny is based on a
single marker, so we expect for it to be not as well resolved as trees from studies
using multiple markers. Although not perfect,
we think the updated phylogeny seems biologically reasonable in different ways. All samples
corresponding to the ingroup cluster together forming a monophyletic group, and
samples belonging to the same \textit{Ilex} species also form
monophyletic groups. A notable exception is \textit{Ilex theeizans}, which appears as
non-monophyletic in the Physcraper updated phylogeny as well as in the original Gottlieb2005 tree.
%This suggests that the samples might represent two different species, but further
analyses should be conducted
A visual comparison of the Yao2020 tree and the original Gottlieb2005 tree suggests
that the relationships within the genus \textit{Ilex} are still being actively
determined, and that increased taxon sampling might be key to resolve them.

@@

@@

\section*{Conclusions}
Data repositories hold more information than meets the eye.
Beyond the main data, they are rich sources of metadata that can be leveraged
for the advantage of all areas of biology as well as the advancement of scientific
policy and applications.
Initial ideas about the data are constantly changed by results from new analyses.
Physcraper provides a framework for reproducible phylogenetics that has the
potential to consistently provide context for these ideas, highlighting the
importance of data sharing and open science in phylogenetics, biology and science.

@@

\par{\textbf{Project name:} Physcraper}

@@

\par{\textbf{OpenTree:} The Open Tree of Life project}

@@

Code and datasets generated and analysed during the current study are available in
the repositories "physcraper" containing the source code,
\href{https://github.com/McTavishLab/physcraper}{https://github.com/McTavishLab/physcraper};
"physcraperex" containing the examples,
\href{https://github.com/McTavishLab/physcraperex}{https://github.com/McTavishLab/physcraperex};
and, "physcraper\_ms" containing this reproducible manuscript,
\href{https://github.com/McTavishLab/physcraper\_ms}{https://github.com/McTavishLab/physcraper\_ms}.

@@

\section*{Acknowledgements}
We thank the members of the OpenTree development team and the "short bar" Science
and Engineering Building 1, UCM, joint lab paper discussion group for valuable
comments on this manuscript. We also thank the valuable comments of David Posada, Rutger Vos,
and an anonymous reviewer that greatly improved an earlier version of this manuscript.
